Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-08-17 paper/revision/responseToReviewers.tex

\item \emph{I suggest that they only refer to ecoacoustics in the discussion by mentionning that this could be tested on other audio scenes as those recorded in natural environments.}

$\rightarrow$ The abstract introduction, background section and conclusion have been rewritten to widen the scope of application of the proposed method and suggest the ecoacoustic as potential area of interest for further research.

\item \emph{The dataset is too quickly described. I had to read ref\#36 to understand how it was built and made of. It would be nice to have an example of a labelled recording either as a spectrogram or scalogram to estimate the complexity of the scenes recorded. The event classes should also be detailed.}

$\rightarrow$ We have listed the classes from the DCASE taxonomy in full in Section 6.1. In addition, we have included the scalogram of a labeled recording (\emph{park04}) as Figure 3.

@@

\item \emph{The authors present their technique as opposed to the BOF approach, that is considered "state of the art". BOF maybe a popular technique but the fact that gets rid of the temporal structure makes it useless in many tasks. In fact, in DCASE 2013 BOF was the chosen baseline system but no participant proposed that technique. Certainly, BOF allows the authors to make stronger the point about describing an acoustic scene from a few distinct events, but perhaps they should avoid to claim BOF as "the" state of the art in this problem.}

$\rightarrow$
As discussed above in the response to the first reviewer, the application in the DCASE 2013 paper, classification, is different from the one proposed in our work, similarity retrieval. For classification, the BOF approach is indeed not the state of the art. However, in acoustic scene similarity retrieval, we are not aware of any systems which outperform the BOF. As such, it is indeed the state of the art for the similarity retrieval task. The manuscript has been revised to clarify this point.

\item \emph{It would be interesting to see the contribution to the results of the Gammatone wavelet in comparison to Morlet or another more classical wavelet.}

$\rightarrow$ VL $\checkmark$ We have not re-run experiments with Morlet wavelets instead of Gammatone wavelets, for two reasons. First, Morlet wavelets do not fit the whole narrative of the paper as well as Gammatone wavelets: while the arguments in favor of Morlet wavelets arise from harmonic analysis (Heisenberg time-frequency uncertainty tradeoff), those in favor of Gammatone wavelets arise from auditory neurophysiology. Because we work in the context of computational auditory scene analysis, \emph{a fortiori} in an unsupervised setting, we believe that it is preferable to borrow from a well-studied auditory model (Gammatone) rather than from a general-purpose operator (Morlet). The second reason why we did not conduct a systematic benchmark between Morlet and Gammatone is that, in previous experiments involving supervised classification of musical instruments with scattering coefficients, Gammatone wavelets appeared to outperform Morlet wavelets by a small margin, from $80\%$ and $79\%$ test accuracy respectively.
In all likelihood, the effect of the specific choice of wavelet is also small in the case of unsupervised similarity retrieval between auditory scenes, and possibly not statistically significant given the limited sample size of the DCASE 2013 dataset. We have expanded Section 3.4 to highlight these considerations. In addition, we have included a mathematical description of the Gammatone wavelet filter bank employed in this study as supplementary material. Indeed, the design of our Gammatone wavelet is slightly different than in the reference papers of Venkitaraman and Adiga, because, unlike them, we need to account for the influence of both the quality factor $Q$ and the polynomial degree parameter $N$. It is our hope that the proof of the formula linking $Q$ and $N$ to the parameter $\alpha$ in the Gammatone function will be beneficial to the signal processing community at large.
